---
title: "Hands-On Data Excercise"
author: "Ben"
date: "October 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(DT)
```

# Prepare Daily Escapement Data

Escapement data sourced from [Goals data sourced from [Andrew Munro and Eric Volk. 2017. Summary of Pacific Salmon Escapement Goals in Alaska with a Review of Escapements from 2007 to 2015. Knowledge Network for Biocomplexity. doi:10.5063/F1TQ5ZRG](https://knb.ecoinformatics.org/view/doi:10.5063/F1TX3CKH)

```{r}
catch_df <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", method = "libcurl"), stringsAsFactors = FALSE)

head(catch_df)
```


```{r}
catch_BB_df <- catch_df %>%
  filter(SASAP.Region == "Bristol Bay") 

head(catch_BB_df)
```

```{r}
catch_BBSock_df <- catch_BB_df %>%
  filter(Species == "Sockeye") %>% 
  select(SASAP.Region, Location, sampleDate, Species, DailyCount)

head(catch_BBSock_df)
```

```{r}
yearlycatch_BBSock_df <- catch_BBSock_df %>%
  separate(sampleDate, c("year", "month", "day"), "-")

head(yearlycatch_BBSock_df)
```
```{r}
yearlycatchtotal_BBSock_df <- yearlycatch_BBSock_df %>% 
  group_by(Location, year) %>% 
  summarize(total_catch = sum(DailyCount))

head(yearlycatchtotal_BBSock_df)
```



# Prepare Escapement Goals Data

Goals data sourced from [Andrew Munro and Eric Volk. 2017. Summary of Pacific Salmon Escapement Goals in Alaska with a Review of Escapements from 2007 to 2015. Knowledge Network for Biocomplexity. doi:10.5063/F1TQ5ZRG](https://knb.ecoinformatics.org/view/doi:10.5063/F1TQ5ZRG)

```{r}

goals_df <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92014.1", method = "libcurl"), stringsAsFactors = FALSE)

head(goals_df)
```




```{r}
goals_BBSock_df <- goals_df %>%
  filter(Species == "Sockeye", Region == "Bristol Bay") %>% 
  select(Region, System, Species, Lower, Upper, Type, Initial.Year) %>% 
  arrange(System)

head(goals_BBSock_df)
```
```{r}
bb_sockeye_goals <- goals_df %>% 
  filter(Region == "Bristol Bay", Species == "Sockeye") %>% 
  mutate(Lower = as.integer(Lower), Initial.Year = as.integer(Initial.Year)) %>% 
  select(System, Lower, Upper, Initial.Year) %>% 
  drop_na()

datatable(bb_sockeye_goals)
```


Left Join with River as key:

```{r}

#joined_df <- left_join(yearlycatchtotal_BBSock_df, goals_BBSock_df, by = c("Location" = "System"))
joined_df <- left_join(yearlycatchtotal_BBSock_df, bb_sockeye_goals, by = c("Location" = "System"))

head(joined_df)

```



# Evaluate Escapement Goals

```{r ChunkName}
joined_df <- joined_df %>%
  mutate(year = as.numeric(year))  

head(joined_df)
```

```{r}
bb_escapement_with_goals <- joined_df %>% 
  mutate(is_goal_within = ifelse(total_catch < Upper & total_catch > Lower, TRUE, FALSE),
         drop_by_year = ifelse(year >= Initial.Year, FALSE, TRUE))
         
datatable(bb_escapement_with_goals)
```

```{r ChunkName}
joined_df <- joined_df %>%
  mutate(Initial.Year = as.numeric(Initial.Year))%>%
  mutate(year = as.numeric(year))  

head(joined_df)
```
 
 
```{r GoalEval}


```
 
 
 



